Summer 2024 Report

### 2025-02-03 Relations/Report.tex

\begin{table}[h!]
  \centering
  \caption{Local implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, CE-9  & CR, CE-6  & CR , CE-9  & CR, ?  & CR , SN \\
  \hline
  \textbf{RP} & CR, CE-9  & CR, CE-6  & \red{CR} , CE-9 & CR, ?   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 & CR, ?   & \red{CR} , SN \\
  \hline
  \textbf{UN} & CE-3, CE-12  & CE-3, CE-6  & CE-3, CE-9  & CE-3, CE-3  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Local implications - WCR }
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, CE-9  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
  \hline
  \textbf{RP} & CR, CE-9  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & CE-10.1, CE-9  & CR, {CE-6}  & {CE-11} , {CE-9} & CR, ?  & \red{CR} , SN \\
  \hline
  \textbf{UN} & CE-3.1, CE-12  & {CE-3.1}, {CE-6}  & {CE-3.1}, {CE-9}  & {CE-3.1}, {CE-3.1}  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Global implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
  \hline
  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & {CE-11}, {CE-9}  & CR, {CE-6}  & CE-11 , {CE-9} & CR, ?   & \red{CR} , SN \\
  \hline
  \textbf{UN} & {CE-3}, {CE-12} and CE-9  & CR, {CE-6}  & CE-3, {CE-9}  & CR, ?  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Global implications - WCR}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
  \hline
  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & {CR} , {CE-9} & CR, ?   & CR , SN \\
  \hline
  \textbf{WNFP} & CE-1.2, {CE-9}  & CR, {CE-6}  & {CR} , {CE-9} & CR, ?   & CR , SN \\
  \hline
  \textbf{UN} & CE-1.1, {CE-9}  & CR, {CE-6}  & {CR}, {CE-9}  & CR, ?  & CR , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

>>>>

\begin{table}[h!]
  \centering
  \caption{Local implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, CE-9  & CR, CE-6  & CR , CE-9  & CR, SN  & CR , SN \\
  \hline
  \textbf{RP} & CR, CE-9  & CR, CE-6  & \red{CR} , CE-9 & CR, SN   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 & CR, SN   & \red{CR} , SN \\
  \hline
  \textbf{UN} & CE-3, CE-12  & CE-3, CE-6  & CE-3, CE-9  & CE-3, CE-3  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Local implications - WCR }
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, CE-9  & CR, {CE-6}  & CR , {CE-9}  & CR, SN  & CR , SN \\
  \hline
  \textbf{RP} & CR, CE-9  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, SN   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & CE-10.1, CE-9  & CR, {CE-6}  & {CE-11} , {CE-9} & CR, SN  & \red{CR} , SN \\
  \hline
  \textbf{UN} & CE-3.1, CE-12  & {CE-3.1}, {CE-6}  & {CE-3.1}, {CE-9}  & {CE-3.1}, {CE-3.1}  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Global implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, SN  & CR , SN \\
  \hline
  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, SN   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & {CE-11}, {CE-9}  & CR, {CE-6}  & CE-11 , {CE-9} & CR, SN   & \red{CR} , SN \\
  \hline
  \textbf{UN} & {CE-3}, {CE-12} and CE-9  & CR, {CE-6}  & CE-3, {CE-9}  & CR, SN  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Global implications - WCR}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, SN  & CR , SN \\
  \hline
  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & {CR} , {CE-9} & CR, SN   & CR , SN \\
  \hline
  \textbf{WNFP} & CE-1.2, {CE-9}  & CR, {CE-6}  & {CR} , {CE-9} & CR, SN   & CR , SN \\
  \hline
  \textbf{UN} & CE-1.1, {CE-9}  & CR, {CE-6}  & {CR}, {CE-9}  & CR, SN  & CR , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}
